### 2015-06-15 Paper_Markdown.Rmd
Working on cleaning things up for writing.  Moved figure 3 over to a function in its own file.

---
output: word_document
---
Non-analogues in paleoecological reconstruction - the effects of analogue distance
========================================================

@@

Mean minimum dissimilarity for pollen samples in the modern pollen dataset ranges from `r min(min.diss)` to `r min(min.diss)`, with a 95% confidence interval from `r quantile(min.diss, 0.025)` to `r quantile(min.diss, 0.975)`.  The highest minimum analogue distance is for an unpublished site along the New York, Pennsylvannia border.  The site is notable for very high proportions of *Fraxinus pennsylvanica/americana* pollen, more than 5x higher than the next closest site.  The lowest minimum distance occurs across four sites, two from Thinn Lake, identified as potentially anomalous in Williams et al (2009),

@@

mds <- data.frame(pol.mds$points,
                  non.ana = factor(min.diss > 0.48))

non.ana <- ggplot(data = mds, aes(x = X1, y = X2)) +
  geom_point(data = mds[mds$non.ana == FALSE,], alpha=0.5, size = 2, color='black') +   
  geom_point(data = mds[mds$non.ana == TRUE,], alpha=0.7, size = 4, color='red') +
  theme_bw() +
  xlab('MDS Axis One') + ylab('MDS Axis Two') +
  theme(text = element_text(size=24, family='serif'))

non.ana.map <- ggplot(data = data.frame(map), aes(long, lat)) + 
  geom_polygon(aes(group=group), color='blue', alpha=0.2) +
  geom_point(data = data.frame(climate)[mds$non.ana == FALSE,], 
             aes(x = LONDD, y = LATDD), alpha=0.5) +
  geom_point(data = data.frame(climate)[mds$non.ana == TRUE,], 
             aes(x = LONDD, y = LATDD), color = 'red', size = 3) +
   theme_bw() +
  xlab('Longitude') + ylab('Latitude') +
  theme(axis.text=element_text(size=12, family='serif'),
        panel.background = element_rect(fill = 'lightblue')) +
  coord_map(projection='albers', lat0=35, lat1=55, xlim=c(-100, -60), ylim=c(35, 80))

grid.arrange(non.ana, non.ana.map, ncol=2)

@@

ggplot(model.samp, aes(x = dissim, y = preds, group = site, color = init)) +
  geom_path(alpha = 0.1) +
  theme_bw() +
  facet_wrap(~model, nrow = 1) +
  scale_x_continuous(expand=c(0,0), breaks = c(0.5, 1)) +
  scale_y_continuous(expand=c(0,0), limits=c(0, 40)) +
  scale_color_continuous(low = 'blue', high='pink', trans='sqrt') +
  theme(legend.position = 'none',
        axis.title = element_text(family = 'serif', face = 'bold', size = 14),
        strip.text = element_text(family = 'serif', face = 'bold', size = 14),
        axis.text = element_text(family = 'serif', size = 10),
        strip.text = element_text(family = 'serif', face = 'bold', size = 12)) +
  annotate("segment", x=0.48, 
           xend = 0.48, y = 0, yend = 100, size=1, linetype='dashed') +
  xlab('Calibration Dissimilarity') +
  ylab('Predicted Value')

>>>>

---
output: html_document
---
Non-analogues in paleoecological reconstruction - the effects of analogue distance
========================================================

@@

Mean minimum dissimilarity for pollen samples in the modern pollen dataset ranges from `r min(min.diss)` to `r min(min.diss)`, with a 95% confidence interval from `r quantile(min.diss, 0.025)` to `r quantile(min.diss, 0.975)`.  The highest minimum analogue distance is for an unpublished site along the New York, Pennsylvannia border.  The site is notable for very high proportions of *Fraxinus pennsylvanica/americana* pollen, more than 5x higher than the next closest site.  The lowest minimum distance occurs across four sites, two from Thinn Lake, identified as potentially anomalous in Williams et al (2009) and XXXX.  The geographic distribution of non-analogue sites is particularly interesting since many of the sites are in close proximity to other modern sites.  This indicates that While spatial autocorreltaion is likely to play a role in the proximity of analogues (and thus their predictions) [@telfordSpatialAuto] it is not always the case that spatially proximate samples are compositionally proximate.

@@

source('R/figures/figure3.R')
run_figure3(pol.mds, min.diss, map, climate)

@@

ggplot(model.samp, aes(x = dissim, y = preds, group = site, color = init)) +
  geom_path(alpha = 0.1) +
  theme_bw() +
  facet_wrap(~model, nrow = 1) +
  scale_x_continuous(expand=c(0,0), breaks = c(0.5, 1)) +
  scale_y_continuous(expand=c(0,0), limits=c(0, 40)) +
  #scale_color_continuous(low = 'blue', high='pink', trans='sqrt') +
  theme(legend.position = 'none',
        axis.title = element_text(family = 'serif', face = 'bold', size = 14),
        strip.text = element_text(family = 'serif', face = 'bold', size = 14),
        axis.text = element_text(family = 'serif', size = 10),
        strip.text = element_text(family = 'serif', face = 'bold', size = 12)) +
  annotate("segment", x=0.48, 
           xend = 0.48, y = 0, yend = 100, size=1, linetype='dashed') +
  xlab('Calibration Dissimilarity') +
  ylab('Predicted Value')
